
\documentclass[10pt]{article}

\usepackage{url}

% This is a helpful package that puts math inside length specifications
\usepackage{calc}


\usepackage[backend=bibtex, style=nature, sorting=ydnt, firstinits=true, maxnames=99]{biblatex}
\setlength\bibitemsep{\baselineskip}
%\DeclareNameAlias{author}{last-first}
\DeclareLanguageMapping{american}{american-apa}
\newcommand{\dn}[1]{{\color{black} {#1}}}


\AtDataInput{%
	\csnumgdef{entrycount:\therefsection}{%
		\csuse{entrycount:\therefsection}+1}}

% Print the labelnumber as the total number of entries in the
% current refsection, minus the actual labelnumber, plus one
\DeclareFieldFormat{labelnumber}{\mkbibdesc{#1}}    
\newrobustcmd*{\mkbibdesc}[1]{%
	\number\numexpr\csuse{entrycount:\therefsection}+1-#1\relax}


\addbibresource{bibtex20180531.bib}
%\bibliographystyle{apalike}
% Layout: Puts the section titles on left side of page
\reversemarginpar

%
%         PAPER SIZE, PAGE NUMBER, AND DOCUMENT LAYOUT NOTES:
%
% The next \usepackage line changes the layout for CV style section
% headings as marginal notes. It also sets up the paper size as either
% letter or A4. By default, letter was used. If A4 paper is desired,
% comment out the letterpaper lines and uncomment the a4paper lines.
%
% As you can see, the margin widths and section title widths can be
% easily adjusted.
%
% ALSO: Notice that the includefoot option can be commented OUT in order
% to put the PAGE NUMBER *IN* the bottom margin. This will make the
% effective text area larger.
%
% IF YOU WISH TO REMOVE THE ``of LASTPAGE'' next to each page number,
% see the note about the +LP and -LP lines below. Comment out the +LP
% and uncomment the -LP.
%
% IF YOU WISH TO REMOVE PAGE NUMBERS, be sure that the includefoot line
% is uncommented and ALSO uncomment the \pagestyle{empty} a few lines
% below.
%

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactenum will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers

\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}{0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                   \arabic{page} of \protect\pageref*{LastPage} 
                   \hfill \,}}
               
\rfoot{\hspace{\footpageshift}%
	\parbox{4in}{\, \hfill %
		\today
		\hfill \,}}
                
%\lfoot{\hspace{\footpageshift}%
%	\parbox{6in}{\, \hfill %
%		\today % +LP
		%                    \arabic{page}                               % -LP
%		\hfill \,}}

%\fancyfoot[c]{\arabic{page} of \protect\pageref*{LastPage}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\fancyhead[LO,LE]{\bf Boyi Guo}
%\fancyhead[RO,RE]{\bf \today}

\fancyheadoffset{\marginparsep + \marginparwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}
%\fancyhead[LO,LE]{\makeheading{Dustin M. Long}}
% The section headings
%
% Usage: \section{section name}
%
% Follow this section IMMEDIATELY with the first line of the section
% text. Do not put whitespace in between. That is, do this:
%
%       \section{My Information}
%       Here is my information.
%
% and NOT this:
%
%       \section{My Information}
%
%       Here is my information.
%
% Otherwise the top of the section header will not line up with the top
% of the section. Of course, using a single comment character (%) on
% empty lines allows for the function of the first example with the
% readability of the second example.
\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{enumerate}[#1]}{\end{enumerate}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactenum}[#1]}{\end{compactenum}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage{natbib}
%\bibliographystyle{plainnat}
\begin{document}
%\thispagestyle{empty}
\makeheading{Boyi Guo, Ph.D.}

\section{Contact Information}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table 
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{1.85in}%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
\href{https://publichealth.jhu.edu/departments/biostatistics}{Department of Biostatistics} &
Email: \href{mailto:bguo6@jhu.edu}{bguo6@jhu.edu}\\
\href{https://publichealth.jhu.edu/}{Bloomberg School of Public Health}	&
GitHub: \href{https://twitter.com/boyiguo}{boyiguo1}	\\
\href{https://www.jhu.edu/}{Johns Hopkins University}&
Website: \href{https://boyiguo1.github.io/}{boyiguo1.github.io}	\\
615 N Wolfe St 
& Phone: (217) 419-9519\\
Baltimore, MD 21205   USA           
& Prounouns: he/his \\
\end{tabular}


\section{Research Statement} I am interested in developing computational tools to conduct quantitative analysis of biomedical data that is often high-volume and high-variety. Specifically, my research addresses statistical challenges in exploring human health at the population and -omics levels to improve disease prognosis and prevention. 



\section{Education \& Training}
%
\href{https://www.jhu.edu/}{\textbf{Johns Hopkins University}}, 
Baltimore, Maryland, USA
\begin{outerlist}
		\item[] Postdoctoral Fellow,
        \href{https://publichealth.jhu.edu/departments/biostatistics}
             {Biostatistics}, 
        \begin{innerlist}
        \item Mentor: \href{https://www.stephaniehicks.com/}{Stephanie Hicks, Ph.D.} \\
		\end{innerlist}
\end{outerlist}

\href{http://www.uab.edu/}{\textbf{University of Alabama at Birmingham}}, 
Birmingham, Alabama, USA
\begin{outerlist}
		\item[] Ph.D., 
        \href{https://www.soph.uab.edu/bst}
             {Biostatistics}, July 2022
        \begin{innerlist}
        %%Dissertation topic here
        \item {Dissertation Topic: {\it Bayesian Hierarchical Additive Models in High Dimensional Data Analysis}}
        \item Advisor: Nengjun Yi, Ph.D. \\
		\end{innerlist}
\end{outerlist}

\href{http://illinois.edu/}{\textbf{University of Illinois at Urbana-Champaign}}, 
Champaign, Illinois, USA
\begin{outerlist}
\item[] M.S., 
        \href{https://stat.illinois.edu/}
             {Statistics}, May 2017
        \begin{innerlist}
        \item Thesis Topic: {\it Estimating Heterogeneous Treatment Effect on Multivariate Responses Using Random Forests}
      \item Advisor: {Ruoqing Zhu, Ph.D.}
        \end{innerlist}
\item[] B.S., 
        \href{https://stat.illinois.edu/}
             {Statistics}, May 2014
                \begin{innerlist}        
             	%\item \emph{Cum Laude}
             	\item Graduated with Highest Distinction
             \end{innerlist}
\item[] B.S., 
        \href{https://cs.illinois.edu/}
             {Computer Science}, May 2014
        \begin{innerlist}        
        %\item \emph{Cum Laude}
        \item Minor in Mathematics
        \end{innerlist}
\end{outerlist}





\section{Research Experience}
\href{http://www.uab.edu/}{\textbf{University of Alabama at Birmingham}}
\begin{outerlist}
	\item[] \textit{\bf Graduate Research Assistant} \normalfont% 
	\hfill \textbf{December 2018 to July 2022}
		\begin{innerlist}
		\item Biostatistician for \href{http://www.regardsstudy.org/home}{REGARDS (REasons for Geographic and Racial Differences in Stroke)} cohort study
		
		\textit{Conduct statistical analysis in R, specializing mediation analysis, inverse probability weighting; draft analysis proposal and manuscript}

	\end{innerlist}
	
\end{outerlist}

\blankline

\href{https://stat.illinois.edu/}{\textbf{University of Illinois at Urbana-Champaign Department of Statistics}}
\begin{outerlist}
\item[] \textit{\bf Graduate Research Assistant} \normalfont% 
        \hfill \textbf{August 2014 to August 2017}
        \begin{innerlist}
		\item Tree Methods for Personalized Treatment
		
		 \textit{Implemented microbiome data analysis for dietary data; developed a tree-based learning framework for individualized treatment effect estimation}\\
		 
		\item GWAS Sample Size Estimation
		
		\textit{Drafted statistical analysis plan and sample size calculation to support proposal}\\
		
		\item Statistical Consultant
		
		\textit{Provided statistical analysis support;administrated online survey study}
		\end{innerlist}
\end{outerlist}

\blankline

\href{http://www.dowagro.com/en-US}{\textbf{Dow AgroSciences}}
\begin{outerlist}
	\item[] \textit{\bf Intern in Computational Biology} \normalfont%         
	\hfill \textbf{August 2016 to May 2017}
	
    \textit{Performed statistics analysis on proteomics data; Developed an R Shiny program for data analysis and interactive visualization}
\end{outerlist}




%%%%%% Publication Section %%%%%%%%%%%
\input{Publications}

\section{Presentations: Scientific Meetings}

\textbf{Guo, B.}, Yi, N. {\it A Scalable and Flexible Cox Proportional Hazard Model for High-Dimensional Survival Prediction and Functional Selection.} Eastern North American Region of the International Biometric Society, Nashville, TN. March 20, 2023\\

\textbf{Guo, B.}, Yi, N. {\it A Scalable and Flexible Cox Proportional Hazard Model for High-Dimensional Survival Prediction and Functional Selection.} Joint Statistical Meetings, Washington, DC. August 8, 2022\\

\textbf{Guo, B.}, Yi, N. {\it Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data.} Eastern North American Region of the International Biometric Society, Houston, TX. March 28, 2022\\

\textbf{Guo, B.}, Yi, N.  {\it Spike-and-Slab Generalized Additive Models and Fast Algorithms for High-Dimensional Data.} Joint Statistical Meetings, Virtual. August 8, 2021\\

\textbf{Guo, B.}, Yi, N. {\it Prediction and Variable Selection Using Network-integrated Spike-and-slab Gaussian Model.} Eastern North American Region of the International Biometric Society, Virtual. March 16, 2021\\

\textbf{Guo, B.},  Zhu, R. {\it Estimating optimal treatment regimes using multivariate random forests,} 3rd ASA Alabama Chapter Mini-Conference, Oxford, MS. April 5, 2019\\

\textbf{Guo, B.},  Zhu, R. {\it Estimating optimal treatment regimes using multivariate random forests,} Eastern North American Region of the International Biometric Society, Philadelphia, PA. March 25, 2019\\

\section{Presentations: Invited \& Lab}
\textbf{Guo, B.}  {\it Calculating Residential Segregation Indices in a Reproducible Pipeline.} REGARDS Analyst Meeting, Virtual. February 17, 2022\\

\textbf{Guo, B.}  {\it Precision Medicine Research Using Statistical Learning Methods.} Hansen and Hicks Joint Lab Meeting, Johns Hopkins University, Virtual. August 25, 2021\\

\textbf{Guo, B.}  {\it Three Levels of Splines: Understanding, Application and Beyond.} REGARDS Analyst Meeting, Virtual. April 8, 2021\\

\textbf{Guo, B.}  {\it All You Wanted to Know About Splines.} University of Vermont, Department of Medicine, REGARDS Lab Meeting, Virtual. February 16, 2021\\

\textbf{Guo, B.}  {\it Using Stratified Cox Regression to Test Competing Risks.} REGARDS Analyst Meeting, Virtual. November 19, 2020\\

\textbf{Guo, B.}  {\it Reproducible Data Analysis Workflow.} REGARDS Analyst Meeting, Virtual. July 16, 2020\\

\textbf{Guo, B.}  {\it Automating Table One.} Department of Biostatistics Professional Development Series, Virtual. June 23, 2020\\

\textbf{Guo, B.}  {\it A visit to `Could Fisher, Jeffreys and Neyman have agreed on testing?} UAB Department of Biostatistics Journal Club, Birmingham, AL. April 19, 2019\\

\textbf{Guo, B.}  {\it Individualized treatment and machine learning.} UAB School of Public Health National Public Health Week Student Research Seminar, Birmingham, AL. April 5, 2018\\

\section{Contributed Presentations \& Posters}($^\ast$ denotes presenter)\\

Mukaz D. K.$^\ast$, \textbf{Guo B.}, Long, D. L., Judd S. E., Plante, T. B., McClure, L. A., ... \& Cushman M. {\it D-dimer and the Risk of Hypertension: The REasons for Geographic and Racial Differences in Stroke (REGARDS).} ISTH 2021, Virtual. June 30, 2021\\

Malla G.$^\ast$, Long D. L., Cherrington A., Goyal P., \textbf{Guo B.}, Safford M. M., Khodneva Y., Cummings D. M., McAlexander T. P., DeSilva S., Judd S. E., Hidalgo B., Levitan E. B., Carson A. P. {\it Neighborhood Social And Economic Environment and Heart Failure Risk.} AHA EpiLifestyle, Vitual. May 21, 2021\\

Long, D. L.$^\ast$, Jaeger, B. C., \textbf{Guo, B.} {\it Sampling Design Considerations for Nested Biomarker Studies.} Eastern North American Region of the International Biometric Society, Virtual. March 15, 2021\\

Pendegraft, A. H.$^\ast$, \textbf{Guo, B.}, Yi, N., {\it Hierarchical negative binomial models applied to high-dimensional human microbiome count data.} Eastern North American Region of the International Biometric Society, Atlanta, GA. March 22, 2018\\

\input{Awards}

\section{Teaching Experience}
\href{https://www.jhu.edu/}{\textbf{Johns Hopkins University}}
\begin{outerlist}
	
	\item[] \textit{\bf Guest Lecturer} \normalfont% 
		\begin{innerlist}
  
		\item \href{https://www.stephaniehicks.com/jhustatprogramming2022/}{BST 840: Statistical Programming Paradigms and Workflows} (2 Lecture) \hfill Fall 2022\\
			\textit{Created course notes and delivered lectures on \href{https://www.stephaniehicks.com/jhustatprogramming2022/posts/2022-11-29-purrr-fun-programming/}{functional programming with \texttt{purrr}}, \href{https://www.stephaniehicks.com/jhustatprogramming2022/posts/2022-12-01-pkgdown-pkg-website/}{website development with \texttt{pkgdown}} and \href{https://www.stephaniehicks.com/jhustatprogramming2022/posts/2022-12-01-targets-proj-workflows/}{workflow construction with \texttt{targets}}.}
	\end{innerlist}	
\end{outerlist}

\blankline

\href{http://www.uab.edu/}{\textbf{University of Alabama at Birmingham}}
\begin{outerlist}
	
	\item[] \textit{\bf Graduate Teaching Assistant} \normalfont% 
		\begin{innerlist}
		\item BST 625: Design and Conduct Clinical Trials	\hfill Summer 2020
		
			\textit{Developed grading rubric for homework and provided feedback; independently curated review material for lectures}
	    \end{innerlist}

	\item[] \textit{\bf Guest Lecturer} \normalfont% 
		\begin{innerlist}
  		\item BST 680: Statistical Computing with R (2 Lectures) \hfill Summer 2022\\
		    \textit{Lectured on data wrangling with \texttt{dplyr} and led hands-on data practice}
		\item BST 655: Categorical Data Analysis (1 Lecture) \hfill Fall 2019\\
			\textit{Delivered the lecture on the topic of model specification and interpretation}
	\end{innerlist}	
\end{outerlist}

\section{Tutorials}	
\textbf{Guo, B.} (2022) Calculating Residential Segregation Indices with Decennial US Census Data in an R Reproducible Workflow\\ \url{https://tinyurl.com/5n8swme3}\\

\textbf{Guo, B.}, Cui, J. (2021) Automating Simulation Studies with High-performance Computation Platform\\ \url{https://tinyurl.com/2p97d2zs}

\section{Mentoring}
\vspace{-3ex}

Jinhong Cui, Doctoral student in Biostatsitics, University of Alabama at Birmingham\\
\textit{Mentor academic writing; co-authored manuscripts and tutorials}\\

Linzi Li, Doctoral student in Epidemiology, Emory University\\
\textit{Help with career development planning; mentor on graduate school application.}\\

Mokshad P Gaonkar, Doctoral student in Biostatsitics, University of Alabama at Birmingham\\
\textit{Provide suggestions for curriculum design}
    


\section{Service: Academic}
%
{University of Alabama at Birmingham}
\begin{outerlist}%\item[]
%\begin{innerlist}
\item Chair, Professional Development and Leadership Committee \hfill 2019 - 2021
\item Student Senator, Graduate Student Government \hfill 2018 - 2022
\item Student Representative, Graduate Program Committee \hfill 2018 - 2019
\item Biostatistics Senator, Public Health Student Association \hfill 2017 - 2019
%\end{innerlist}
\end{outerlist}

\blankline

{University of Illinois at Urbana-Champaign}
\begin{outerlist}%\item[]
%\begin{innerlist}
\item Illinois International Advisory Committee\hfill 2016 - 2017
%\end{innerlist}
\end{outerlist}

\section{Service: Program}
{IEEE Conference on Computational Intelligence in Bioinformatics and Computational Biology}
\begin{outerlist}
\item Manuscript reviewer \hfill 2023
\end{outerlist}



{International Biometric Society (Eastern North American Region)}
\begin{outerlist}
\item Session chair on \textit{Contributed Papers: High Dimensional Data} \hfill 2022
\item Session chair on \textit{Contributed Papers: Spatial, Spatial-temporal and Graphic Modeling} \hfill 2021
\end{outerlist}

\section{Service: Peer Review}
\begin{lonelist}
\item Nature Methods
\item Genome Biology
\item Statistical Methods in Medical Research
\item Mayo Clinic Proceedings
\end{lonelist}
\blankline


\section{Professional Memberships}
\begin{lonelist}
	\item American Statistical Association
	\item International Chinese Statistical Association
	\item International Biometric Society (Eastern North American Region)
	\item Phi Kappa Phi
\end{lonelist}
%\end{outerlist}
\blankline

\section{Certifications}
\begin{lonelist}
    \item Statistical Horizons Causal Mediation Analysis by Tyler VanderWeele \hfill 2022
	\item SAS Certified Base Programmer for SAS 9 Credential\hfill 2014
	\item Oracle Certified Associate Java SE 7 Programmer\hfill 2014
\end{lonelist}

\blankline

\section{Other}
{University of Illinois at Urbana-Champaign}
\begin{outerlist}\item[]
	\begin{innerlist}
		\item University Varsity in Illini Rowing Team \hfill 2011 - 2012
	\end{innerlist}
\end{outerlist}


\section{Keywords} High-dimensional Data Analysis, Integrative Data Analysis, Bayesian Hierarchical Models, Statistical Learning, Precision Medicine
%\input{Reference}
\end{document}
