


\documentclass[10pt]{article}

% This is a helpful package that puts math inside length specifications
\usepackage{calc}


\usepackage[backend=bibtex, style=nature, sorting=ydnt, firstinits=true, maxnames=99]{biblatex}
\setlength\bibitemsep{\baselineskip}
%\DeclareNameAlias{author}{last-first}
\DeclareLanguageMapping{american}{american-apa}



\AtDataInput{%
	\csnumgdef{entrycount:\therefsection}{%
		\csuse{entrycount:\therefsection}+1}}

% Print the labelnumber as the total number of entries in the
% current refsection, minus the actual labelnumber, plus one
\DeclareFieldFormat{labelnumber}{\mkbibdesc{#1}}    
\newrobustcmd*{\mkbibdesc}[1]{%
	\number\numexpr\csuse{entrycount:\therefsection}+1-#1\relax}


\addbibresource{bibtex20180531.bib}
%\bibliographystyle{apalike}
% Layout: Puts the section titles on left side of page
\reversemarginpar

%
%         PAPER SIZE, PAGE NUMBER, AND DOCUMENT LAYOUT NOTES:
%
% The next \usepackage line changes the layout for CV style section
% headings as marginal notes. It also sets up the paper size as either
% letter or A4. By default, letter was used. If A4 paper is desired,
% comment out the letterpaper lines and uncomment the a4paper lines.
%
% As you can see, the margin widths and section title widths can be
% easily adjusted.
%
% ALSO: Notice that the includefoot option can be commented OUT in order
% to put the PAGE NUMBER *IN* the bottom margin. This will make the
% effective text area larger.
%
% IF YOU WISH TO REMOVE THE ``of LASTPAGE'' next to each page number,
% see the note about the +LP and -LP lines below. Comment out the +LP
% and uncomment the -LP.
%
% IF YOU WISH TO REMOVE PAGE NUMBERS, be sure that the includefoot line
% is uncommented and ALSO uncomment the \pagestyle{empty} a few lines
% below.
%

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactenum will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers

\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}{0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                   \arabic{page} of \protect\pageref*{LastPage} 
                   \hfill \,}}
               
\rfoot{\hspace{\footpageshift}%
	\parbox{4in}{\, \hfill %
		\today
		\hfill \,}}
                
%\lfoot{\hspace{\footpageshift}%
%	\parbox{6in}{\, \hfill %
%		\today % +LP
		%                    \arabic{page}                               % -LP
%		\hfill \,}}

%\fancyfoot[c]{\arabic{page} of \protect\pageref*{LastPage}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\fancyhead[LO,LE]{\bf Dustin M. Long}
%\fancyhead[RO,RE]{\bf \today}

\fancyheadoffset{\marginparsep + \marginparwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}
%\fancyhead[LO,LE]{\makeheading{Dustin M. Long}}
% The section headings
%
% Usage: \section{section name}
%
% Follow this section IMMEDIATELY with the first line of the section
% text. Do not put whitespace in between. That is, do this:
%
%       \section{My Information}
%       Here is my information.
%
% and NOT this:
%
%       \section{My Information}
%
%       Here is my information.
%
% Otherwise the top of the section header will not line up with the top
% of the section. Of course, using a single comment character (%) on
% empty lines allows for the function of the first example with the
% readability of the second example.
\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{enumerate}[#1]}{\end{enumerate}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactenum}[#1]}{\end{compactenum}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage{natbib}
%\bibliographystyle{plainnat}
\begin{document}

\makeheading{Boyi Guo, M.S.}

\section{Contact Information}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table 
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{1.85in}%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
\href{https://www.soph.uab.edu/bst}{Department of Biostatistics}  	&\textit{Cell:} (217) 419-9519\\
\href{https://www.soph.uab.edu}{Ryals School of Public Health}	&\href{mailto:boyiguo1@uab.edu}{boyiguo1@uab.edu}\\
\href{https://www.uab.edu/home/}{University of Alabama at Birmingham}\\
514 Ryals Public Health Building		\\
1665 University Blvd                     \\
Birmingham, AL 35294-0002   USA           & \\
\end{tabular}


\section{Research Interests}
Bayesian Data Analysis, High Dimensional Data Analysis, Statistical Learning, Causal Inference

\section{Education}
%
\href{http://www.uab.edu/}{\textbf{University of Alabama at Birmingham}}, 
Birmingham, Alabama, USA
\begin{outerlist}
		\item[] Ph.D., 
        \href{https://www.soph.uab.edu/bst}
             {Biostatistics}, May 2022 (Expected)
        \begin{innerlist}
        %%Dissertation topic here
        \item {Dissertation Topic: ``Bayesian Hierarchical Spline Models in High Dimensional Data Analysis''}
        \item Advisor: Nengjun Yi, Ph.D. \\
		\end{innerlist}
\end{outerlist}

\href{http://illinois.edu/}{\textbf{University of Illinois at Urbana-Champaign}}, 
Champaign, Illinois, USA
\begin{outerlist}
\item[] M.S., 
        \href{https://stat.illinois.edu/}
             {Statistics}, May 2017
        \begin{innerlist}
        \item Thesis Topic: ``Estimating Optimal Treatment Regimes Using Multivariate Response Random Forests''
       \item Advisor: {Ruoqing Zhu, Ph.D.}\\
        \end{innerlist}
\end{outerlist}

\href{http://illinois.edu/}{\textbf{University of Illinois at Urbana-Champaign}}, 
Champaign, Illinois, USA
\begin{outerlist}
\item[] B.S., 
        \href{https://stat.illinois.edu/}
             {Statistics}, May 2014
                \begin{innerlist}        
             	%\item \emph{Cum Laude}
             	\item Graduated with Highest Distinction
             \end{innerlist}
\item[] B.S., 
        \href{https://cs.illinois.edu/}
             {Computer Science}, May 2014
        \begin{innerlist}        
        %\item \emph{Cum Laude}
        \item Minor in Mathematics
        \end{innerlist}
\end{outerlist}

\section{Awards} 
\href{http://www.uab.edu/}{\textbf{University of Alabama at Birmingham}}
\begin{outerlist}\item[]
\begin{innerlist}
\item UAB Outstanding Graduate Scholastic Achievement Award \hfill 2021
\item UAB Blazer Way Award \hfill 2020
\item Graduate Student Government Travel Grant\hfill 2019, 2020
\item ASA Alabama Chapter Student Research Award \hfill 2019
\item Dr. Al M Best Biostatistics Teaching Award \hfill 2019
\item Outstanding Senator of The Year \hfill 2019
\item Blazer Graduate Research Fellowship\hfill 2017 - 2018
\end{innerlist}
\end{outerlist}

\section{Teaching Experience}
\href{http://www.uab.edu/}{\textbf{University of Alabama at Birmingham}}
\begin{outerlist}
	
	\item[] \textit{\bf Graduate Teaching Assistant} \normalfont% 
		\begin{innerlist}
		\item BST 625: Design and Conduct Clinical Trials	\hfill Summer 2020
		
			\textit{Developed grading rubric for homework and provided feedback; independently curated review material for lectures}
	    \end{innerlist}

	\item[] \textit{\bf Guest Lecturer} \normalfont% 
		\begin{innerlist}
		\item BST 655: Categorical Data Analysis (1 Lecture) \hfill Fall 2019
	\end{innerlist}	
	
\end{outerlist}

\section{Research Experience}
\href{http://www.uab.edu/}{\textbf{University of Alabama at Birmingham}}
\begin{outerlist}
	\item[] \textit{\bf Graduate Research Assistant} \normalfont% 
	\hfill \textbf{December 2018 to Present}
		\begin{innerlist}
		\item Biostatistician for \href{http://www.regardsstudy.org/home}{REGARDS (REasons for Geographic and Racial Differences in Stroke)} study
		
		\textit{Conduct statistical analysis in R, specializing mediation analysis, inverse probability weighting; draft analysis proposal and manuscript}

	\end{innerlist}
	
\end{outerlist}

\blankline

\href{https://stat.illinois.edu/}{\textbf{University of Illinois at Urbana-Champaign Department of Statistics}}
\begin{outerlist}
\item[] \textit{\bf Graduate Research Assistant} \normalfont% 
        \hfill \textbf{August 2014 to August 2017}
        \begin{innerlist}
		\item Tree Methods for Personalized Treatment
		
		 \textit{Implemented microbiome data analysis for dietary data; developed a tree-based learning framework for treatment recommendation}\\
		 
		\item GWAS Sample Size Estimation
		
		\textit{Drafted statistical analysis plan and sample size calculation to support proposal writing}\\
		
		\item Statistical Consultant
		
		\textit{Provided statistical analysis support;administrated online survey study}
		\end{innerlist}
\end{outerlist}


\section{Work Experience}
\href{http://www.dowagro.com/en-US}{\textbf{Dow AgroSciences}}
\begin{outerlist}
	\item[] \textit{\bf Intern in Computational Biology} \normalfont%         
	\hfill \textbf{August 2016 to May 2017}
	
    \textit{Performed statistics analysis on proteomics data; Developed an R Shiny program for data analysis and interactive visualization}
\end{outerlist}

\blankline



\section{Peer-Reviewed Publications}

\vspace{-3ex}

\nocite{*}
\printbibliography[heading=none]
11. \textbf{Guo, B.}, Zhu, R., Holscher, L. S., Auvil, L. S., Welge, M. E., Bushell, C. B., Baer, D. J., Novotny, J. A., ``Estimating optimal treatment regimes using multivariate response random forests" \textit{Statistics in BioSciences, accepted} (2021)\\

10. Cummings, D. M., Patil, S. P., Long, D. L., \textbf{Guo, B.}, Cherrington, A., Safford, M. M., Judd, S. E., Howard, V. J., Howard, G., Carson, A. P. Does the Association between Hemoglobin A1c and Risk of Cardiovascular (CVD) Events vary by Residential Segregation? The Reasons for Geographic and Racial Differences in Stroke (REGARDS) Study. \textit{Diabetes Care, in press.} (2020).\\

9. Plante, T. B., Long, D. L., \textbf{Guo, B.}, Howard, G., Carson, A. P., Howard, V. J., ... & Cushman, M. C-reactive protein and hypertension incidence in black and white Americans: REasons for Geographic And Racial Differences in Stroke (REGARDS) study. \textit{American journal of hypertension, in press.} (2020). \\

8. Zhang, X., \textbf{Guo, B.}, & Yi, N. ``Zero-Inflated gaussian mixed models for analyzing longitudinal microbiome data," \textit{Plos one, 15(11)}, e0242073. (2020).\\

7. Pendegraft, A. H., \textbf{Guo, B.}, Yi, N. ``Bayesian hierarchical negative binomial models for multivariable analyses with applications to human microbiome count data," \textit{PloS one, 14(8)} (2019). PMID: 31437194\\

6. Seifert, M. E., Gaut, J. P., \textbf{Guo, B.}, Jain, S., Malone, A. F., Geraghty, F., Della Manna, D., Yang, E. S., Yi, N., Brennan, D. C., Mannon, R. B.  ``WNT pathway signaling is associated with microvascular injury and predicts kidney transplant failure," \textit{American Journal of Transplantation} (2019). PMID: 30916889 \\

5. Tang, Z., Lei, S., Zhang, X., Yi, Z., \textbf{Guo, B.}, Chen, J. Y., Shen Y., Yi N.  ``Gsslasso Cox: a Bayesian hierarchical model for predicting survival and detecting associated genes by incorporating pathway information," \textit{BMC bioinformatics, 20(1), 94} (2019). PMID: 30813883\\

4.  Yi, N., Tang, Z., Zhang, X., \textbf{Guo, B.}  ``BhGLM: Bayesian hierarchical GLMs and survival models, with applications to genomics and epidemiology," \textit{Bioinformatics} (2018). PMID: 30219850\\

3. Zhang, X., Pei, Y. F., Zhang, L., \textbf{Guo, B.}, Pendegraft, A., Zhuang, W., Yi, N. ``Negative Binomial Mixed Models for Analyzing Longitudinal Microbiome Data," \textit{Frontiers in microbiology, 9, 1683} (2018). PMID: 30093893\\

2. Bashir, M., Wee, C., Memon, N., \textbf{Guo, B.} ``Profiling cybersecurity competition participants: Self-efficacy, decision-making and interests predict effectiveness of competitions as a recruitment tool," \textit{Computers \& Security, 65, 153-165.} (2017)\\

1. Bashir, M., Lambert, A., \textbf{Guo, B.}, Memon, N., Halevi, T. ``Cybersecurity competitions: The human angle," \textit{IEEE Security \& Privacy, 13(5), 74-79} (2015).

\section{In Preparation}

\vspace{-3ex}


Long, D. L., \textbf{Guo, B.}, McClure, L. A., Jaeger, B. C., Tison, S., Howard, G., Judd, S. E., Howard, V. J., Plante, T. B., Zakai, N. , Koh, I., Cheung, K. L., Cushman, M., ``Biomarkers as MEDiators of racial disparities in Risk factors (BioMedioR): rationale, study design and statistical considerations" (Submitted to \textit{American Journal of Epidemiology})\\

Jaeger, B. C., \textbf{Guo, B.}, ``R-squared and goodness of fit in the linear mixed model: A cautionary tale"

\section{Abstracts}

Peper, K. M., \textbf{Guo, B.}, Long, L., Howard, G., Carson, A. P., Howard, V. J., ... & Plante, T. B.  ``C-reactive Protein and Racial Differences in Type 2 Diabetes Incidence: Reasons for Geographic and Racial Differences in Stroke (REGARDS)," \textit{Circulation, 141, AP300-AP300.} (2020).\\

Subramaniam, A., \textbf{Guo, B.}, Lobashevsky, E., van der Pol, W., Lefkowitz, E., Morrow, C., ... & Owen, J.  ``Are cervicovaginal microbiome differences associated with cerclage success in high-risk women with cervical shortening?" \textit{American Journal of Obstetrics & Gynecology, 222(1), S123.} (2020)\\

Subramaniam, A., \textbf{Guo, B.}, Lobashevsky, E., van der Pol, W., Lefkowitz, E., Morrow, C., ... & Owen, J.  ``Longitudinal changes in the cervicovaginal microbiome in high-risk women who experience midtrimester cervical shortening," \textit{American Journal of Obstetrics & Gynecology, 222(1), S73-S74.} (2020)\\

Subramaniam, A., \textbf{Guo, B.}, Lobashevsky, E., van der Pol, W., Lefkowitz, E., Morrow, C., ... & Owen, J.  ``Association of the cervicovaginal microbiome with cervical shortening in women with prior spontaneous preterm birth," \textit{American Journal of Obstetrics & Gynecology, 222(1), S268-S269.} (2020)\\

Subramaniam, A., \textbf{Guo, B.}, Wetta, L., Lobashevsky, E., van der Pol, W., Lefkowitz, E., ... & Owen, J. `` Association of cervicovaginal microbial changes with pro-and anti-inflammatory biomarkers in cervicovaginal fluid," \textit{American Journal of Obstetrics & Gynecology, 222(1), S15-S16.} (2020)\\

Subramaniam, A., \textbf{Guo, B.}, Lobashevsky, E., van der Pol, W., Lefkowitz, E., Morrow, C., ... & Owen, J. ``Effect of intramuscular progesterone on the cervicovaginal microbiome in high-risk women with midtrimester cervical shortening," \textit{American Journal of Obstetrics & Gynecology, 222(1), S268.} (2020)

\section{Technical Report}
Bashir, M., Lambert, A., Wee, J. M. C., \textbf{Guo, B.}  ``An examination of the vocational and psychological characteristics of cybersecurity competition participants," \textit{In 2015 USENIX Summit on Gaming, Games, and Gamification in Security Education (3GSE '15)} (2015).



\section{Presentations and Poster}($^\ast$ denotes presenter)\\

\textbf{Guo, B.}$^\ast$  ``Three Levels of Splines: Understanding, Application and Beyond,'' REGARDS Analyst Meeting, Birmingham, AL. (April 8, 2021)\\

\textbf{Guo, B.}$^\ast$, Yi, N. ``Prediction and Variable Selection Using Network-integrated Spike-and-slab Gaussian Model,'' Eastern North American Region of the International Biometric Society, Birmingham, AL. (March 16, 2021)\\

Long, D. L.$^\ast$, Jaeger, B. C., \textbf{Guo, B.} ``Sampling Design Considerations for Nested Biomarker Studies,'' Eastern North American Region of the International Biometric Society, Birmingham, AL. (March 15, 2021)\\

\textbf{Guo, B.}$^\ast$  ``All You Wanted to Know About Splines,'' University of Vermont, Department of Medicine, REGARDS Lab Meeting, Birmingham, AL. (February 16, 2021)\\

\textbf{Guo, B.}$^\ast$  ``Using Stratified Cox Regression to Test Competing Risks,'' REGARDS Analyst Meeting, Birmingham, AL. (November 19, 2020)\\

\textbf{Guo, B.}$^\ast$  ``Reproducible Data Analysis Workflow,'' REGARDS Analyst Meeting, Birmingham, AL. (July 16, 2020)\\

\textbf{Guo, B.}$^\ast$  ``Automating Table One,'' Department of Biostatistics Professional Development Series, Birmingham, AL. (June 23, 2020)\\

\textbf{Guo, B.}$^\ast$  ``A visit to `Could Fisher, Jeffreys and Neyman have agreed on testing?','' Department of Biostatistics Journal Club, Birmingham, AL. (April 19, 2019)\\

\textbf{Guo, B.}$^\ast$,  Zhu, R. ``Estimating optimal treatment regimes using multivariate random forests,'' 3rd ASA Alabama Chapter Mini-Conference, Oxford, MS. (April 5, 2019)\\

\textbf{Guo, B.}$^\ast$,  Zhu, R. ``Estimating optimal treatment regimes using multivariate random forests,'' Eastern North American Region of the International Biometric Society, Philadelphia, PA. (March 25, 2019)\\

\textbf{Guo, B.}$^\ast$  ``Individualized treatment and machine learning,'' National Public Health Week Student Research Seminar, Birmingham, AL. (April 5, 2018)\\

Pendegraft, A. H.$^\ast$, \textbf{Guo, B.}, Yi, N., ``Hierarchical negative binomial models applied to high-fimensional human microobiome count data,'' Eastern North American Region of the International Biometric Society, Atlanta, GA. (March 22, 2018)\\
 
\section{Mentoring}
    Jinhong Cui, Doctoral student, University of Alabama at Birmingham\\
    Linzi Li, Doctoral student, Emory University\\
    Mokshad P Gaonkar, Doctoral student, University of Alabama at Birmingham



\section{Service}
%
{University of Alabama at Birmingham}
\begin{outerlist}\item[]
\begin{innerlist}
\item Chair, Professional Development and Leadership Committee \hfill 2018 - Present
\item Student Senator, Graduate Student Government \hfill 2018 - Present
\item Student Representative, Graduate Program Committee \hfill 2018 - 2019
\item Biostatistics Senator, Public Health Student Association \hfill 2017 - 2019
\end{innerlist}
\end{outerlist}

\blankline

{University of Illinois at Urbana-Champaign}
\begin{outerlist}\item[]
\begin{innerlist}
\item Illinois International Advisory Committee (University) \hfill 2016 - 2017
\end{innerlist}
\end{outerlist}

\section{R pacakges}
\begin{innerlist}
	\item Contributor, TibbleOne
	\item Creator, MOTE.RF
	\item Contributor, BhGLM
\end{innerlist}

\section{Memberships}
\begin{innerlist}
	\item American Statistical Association
	\item American Public Health Association
	\item International Chinese Statistical Association
	\item International Biometric Society (ENAR)
	\item Phi Kappa Phi
\end{innerlist}
%\end{outerlist}

\section{Certifications}
\begin{innerlist}
	\item SAS Certified Base Programmer for SAS 9 Credential\hfill 2014
	\item Oracle Certified Associate Java SE 7 Programmer\hfill 2014
\end{innerlist}


\section{Other}
{University of Illinois at Urbana-Champaign}
\begin{outerlist}\item[]
	\begin{innerlist}
		\item University Varsity in Illini Rowing Team \hfill 2011 - 2012
	\end{innerlist}
\end{outerlist}

\end{document}

