\section{Peer-Reviewed Publications}

\vspace{-3ex}

% \nocite{*}
% \printbibliography[heading=none]

16. Bhave V., Ament Z., Patki A., Gao Y., Kijpaisalratana N., \textbf{Guo B.}, Chaudhary N., Guarniz A. G., Gerszten R., Correa A., Cushman M., Irvin M. R., Judd S. E., Kimberly W. T. (2023) Plasma Metabolites Link the Gut-Brain Axis to Incident Stroke. {\it Annals of Neurology}. {\bf 93}(3):500-510.  doi: \url{https://doi.org/10.1002/ana.26552}\\

15. Mukaz D. K., \textbf{Guo B.}, Long, D. L., Judd S. E., Plante, T. B., McClure, L. A., ...,  Cushman M. (2022). D-dimer and the Risk of Hypertension: The REasons for Geographic and Racial Differences in Stroke (REGARDS). \textit{Research and Practice in Thrombosis and Haemostasis}. {\bf 7}(1):100016. doi: \url{https://doi.org/10.1016/j.rpth.2022.100016}. PMID: 36760775; PMCID: PMC9903654.\\

14. \textbf{Guo, B.}, Jaeger, B. C., Rahman, A. F., Long, D. L., Yi, N. (2022). Spike-and-Slab least absolute shrinkage and selection operator generalized additive models and scalable algorithms for high-dimensional data analysis. {\it Statistics in Medicine}. {\bf 41}(20): 3899– 3914. doi: \url{https://doi.org/10.1002/sim.9483}\\

13. Peper, K. M., \textbf{Guo, B.}, Long, D. L., Howard, G., Carson, A.P., Howard, V.J., Judd, S.E., Zakai, N.A., Cherrington, A., Cushman, M., Plante, T.B. (2022). C-reactive protein and racial differences in type 2 diabetes incidence: The REGARDS study. {\it Journal of Clinical Endocrinology and Metabolism}. {\bf 107}(6), e2523–e2531. doi: \url{https://doi.org/10.1210/clinem/dgac074}\\

12. Long, D. L., \textbf{Guo, B.}, McClure, L. A., Jaeger, B. C., Tison, S., Howard, G., Judd, S. E., Howard, V. J., Plante, T. B., Zakai, N. , Koh, I., Cheung, K. L., Cushman, M. (2021). Biomarkers as MEDiators of racial disparities in Risk factors (BioMedioR): rationale, study design and statistical considerations. \textit{Annals of Epidemiology.} {\bf 66}: 13-19 PMID: 34742867. PMCID: PMC8920757. \\

11. {\bf Guo, B}., Holscher, H. D., Auvil, L. S., Welge, M. E., Bushell, C. B., Novotny, J. A., Baer D. J., Burd, N.A., Khan, N. A., Zhu, R. (2021). Estimating Heterogeneous Treatment Effect on Multivariate Responses Using Random Forests. {\it Statistics in Biosciences.} doi: \url{https://doi.org/10.1007/s12561-021-09310-w}\\

10. Plante, T. B., Long, D. L., \textbf{Guo, B.}, Howard, G., Carson, A. P., Howard, V. J., ... , Cushman, M. (2021). C-reactive protein and hypertension incidence in black and white Americans: REasons for Geographic And Racial Differences in Stroke (REGARDS) study. \textit{American journal of hypertension.} {\bf 34}(7). 698-706. PMID: 33326556. PMCID: PMC8351501. \\

9. Cummings, D. M., Patil, S. P., Long, D. L., {\bf Guo, B.}, Cherrington, A., Safford, M. M., Judd, S. E., Howard, V. J., Howard, G., Carson, A. P. (2021). Does the Association Between Hemoglobin A1c and Risk of Cardiovascular Events Vary by Residential Segregation? The REasons for Geographic And Racial Differences in Stroke (REGARDS) Study. {\it Diabetes Care}, {\bf 44}(5), 1151-1158. PMID: 33958425. PMCID: PMC8132333.\\

8. Zhang, X., {\bf Guo, B.}, Yi, N. (2020). Zero-Inflated gaussian mixed models for analyzing longitudinal microbiome data. {\it Plos one}, {\bf 15}(11), e0242073. PMID: 33166356. PMCID: PMC7652264.\\

7. Pendegraft, A. H., {\bf Guo}, B., Yi, N. (2019). Bayesian hierarchical negative binomial models for multivariable analyses with applications to human microbiome count data. {\it PloS one}, {\bf 14}(8), e0220961. PMID: 31437194. PMCID: PMC6706006.\\

6. Seifert, M. E., Gaut, J. P., {\bf Guo, B.}, Jain, S., Malone, A. F., Geraghty, F., Manna, D. D., Yang, E. S., Yi, N., Brennan, D. C., Mannon, R. B. (2019). WNT pathway signaling is associated with microvascular injury and predicts kidney transplant failure. {\it American Journal of Transplantation}, {\bf 19}(10), 2833-2845. PMID: 30916889. PMCID: PMC6763350. \\

5. Tang, Z., Lei, S., Zhang, X., Yi, Z.,  {\bf Guo, B}, Chen, J. Y., Shen, Y.,  Yi, N. (2019). Gsslasso Cox: a Bayesian hierarchical model for predicting survival and detecting associated genes by incorporating pathway information. {\it BMC bioinformatics}, {\bf 20}(1), 1-15. PMID: 30813883. PMCID: PMC6391807.\\

4. Yi, N., Tang, Z., Zhang, X., {\bf Guo, B.} (2019). BhGLM: Bayesian hierarchical GLMs and survival models, with applications to genomics and epidemiology. {\it Bioinformatics}, {\bf 35}(8), 1419-1421. PMID: 30219850. PMCID: PMC7963076.\\

3. Zhang, X., Pei, Y. F., Zhang, L., {\bf Guo, B.}, Pendegraft, A. H., Zhuang, W., Yi, N. (2018). Negative binomial mixed models for analyzing longitudinal microbiome data. {\it Frontiers in microbiology}, {\bf 9}, 1683. PMID: 30093893. PMCID: PMC6070621.\\

2. Bashir, M., Wee, C., Memon, N., {\bf Guo, B.} (2017). Profiling cybersecurity competition participants: Self-efficacy, decision-making and interests predict effectiveness of competitions as a recruitment tool. {\it Computers \& Security}, {\bf 65}, 153-165. doi: \url{https://doi.org/10.1016/j.cose.2016.10.007}\\

1. Bashir, M., Lambert, A., {\bf Guo, B.}, Memon, N., Halevi, T. (2015). Cybersecurity competitions: The human angle. {\it IEEE Security \& Privacy}, {\bf 13}(5), 74-79. doi: \url{https://doi.org/10.1109/MSP.2015.100}\\

\section{Manuscripts In Preparation}

\vspace{-3ex}

\textbf{Guo, B.}, Hicks, S. C. (2023). \texttt{escheR}: Unified multi-dimensional visualizations with Gestalt principles. {\it bioRxiv}. doi: \url{https://doi.org/10.1101/2023.03.18.533302}\\

Huuki-Myers, L., Spangler, A., Eagles, N., Montgomery, K., Kwon, S., \textbf{Guo, B.}, ..., Collado-Torres, L.,  Maynard, K. R. (2023). Integrated single cell and unsupervised spatial transcriptomic analysis defines molecular anatomy of the human dorsolateral prefrontal cortex. {\it bioRxiv}. doi: \url{https://doi.org/10.1101/2023.02.15.528722}\\

\textbf{Guo, B.}, Yi, N. (2022). A scalable and flexible Cox proportional hazard model for high-dimensional survival prediction and functional selection. {\it arXiv}. doi: \url{https://doi.org/10.48550/arXiv.2205.11600}\\

\textbf{Guo, B.}, Yi, N. (2022). The R Package BHAM: Fast and scalable Bayesian hierarchical additive model for high-dimensional data  {\it arXiv}. doi: \url{https://doi.org/10.48550/arXiv.2207.02348}\\

Cui, J., \textbf{Guo, B.}, Tiwari H., Rahman, F., Sims, A. M., Long, D. L. (2022). Comparison of three mediation methods with survival outcomes via simulation study. (Submitted to \textit{Epidemiologic Methods})\\

\textbf{Guo, B.}, Li, L., Rudolph J. (2023). Statistical thinking in simulation design: a continuing conversation on the balancing intercept problem. {\it arXiv}. doi: \url{ 	
https://doi.org/10.48550/arXiv.2306.11906}\\\\

Malla G., Long D. L., Cherrington A., Goyal P., \textbf{Guo B.}, Safford M. M., Khodneva Y., Cummings D. M., McAlexander T. P., DeSilva S., Judd S. E., Hidalgo B., Levitan E. B., Carson A. P. (2021). Neighborhood Disadvantage and Risk of Heart Failure: The Reasons for Geographic and Racial Differences in Stroke (REGARDS) Study. (In revision for \textit{Circulation: Cardiovascular Quality and Outcomes})\\

\textbf{Guo, B.}, Jaeger, B. C. (2021). R-squared and goodness of fit in the linear mixed model: A cautionary tale. {\it Manuscript per request}\\


\section{Published Abstracts}
Peper, K. M., \textbf{Guo, B.}, Long, L., Howard, G., Carson, A. P., Howard, V. J., ... \& Plante, T. B.  (2020). C-reactive Protein and Racial Differences in Type 2 Diabetes Incidence: Reasons for Geographic and Racial Differences in Stroke (REGARDS). \textit{Circulation}, {\bf 141}, AP300-AP300. \\

Subramaniam, A., \textbf{Guo, B.}, Lobashevsky, E., van der Pol, W., Lefkowitz, E., Morrow, C., ... \& Owen, J.  (2020) Are cervicovaginal microbiome differences associated with cerclage success in high-risk women with cervical shortening? \textit{American Journal of Obstetrics \& Gynecology}, {\bf 222}(1), S123.\\

Subramaniam, A., \textbf{Guo, B.}, Lobashevsky, E., van der Pol, W., Lefkowitz, E., Morrow, C., ... \& Owen, J.  (2020)  Longitudinal changes in the cervicovaginal microbiome in high-risk women who experience midtrimester cervical shortening. \textit{American Journal of Obstetrics \& Gynecology}, {\bf 222}(1), S73-S74.\\

Subramaniam, A., \textbf{Guo, B.}, Lobashevsky, E., van der Pol, W., Lefkowitz, E., Morrow, C., ... \& Owen, J.   (2020) Association of the cervicovaginal microbiome with cervical shortening in women with prior spontaneous preterm birth. \textit{American Journal of Obstetrics \& Gynecology}, {\bf 222}(1), S268-S269.\\

Subramaniam, A., \textbf{Guo, B.}, Wetta, L., Lobashevsky, E., van der Pol, W., Lefkowitz, E., ... \& Owen, J.  (2020) Association of cervicovaginal microbial changes with pro-and anti-inflammatory biomarkers in cervicovaginal fluid. \textit{American Journal of Obstetrics \& Gynecology}, {\bf 222}(1), S15-S16.\\

Subramaniam, A., \textbf{Guo, B.}, Lobashevsky, E., van der Pol, W., Lefkowitz, E., Morrow, C., ... \& Owen, J.  (2020) Effect of intramuscular progesterone on the cervicovaginal microbiome in high-risk women with midtrimester cervical shortening. \textit{American Journal of Obstetrics \& Gynecology}, {\bf 222}(1), S268.\\

\section{Published Articles}

\textbf{Guo, B.}, Samorodnitsky S. (2022) Keep your receipts: A guide for early-career statisticians to navigate conferences’ hidden curriculum. \textit{JEDI Corner, AmstatNews}\\

Bashir, M., Lambert, A., Wee, J. M. C., \textbf{Guo, B.} (2015). An examination of the vocational and psychological characteristics of cybersecurity competition participants. \textit{USENIX Summit on Gaming, Games, and Gamification in Security Education (3GSE '15)}.


\section{Grant Experience: Submitted}
\textit{Computational methods for spatial transcriptomics data integrating multiple omics across multiple samples.}\\[0.0em]
\dn{Institute:}  NIH/NHGRI \hfill \dn{Submission Date:}  2023 Feb\\
\dn{Responsibility:} Principal Investigator






\section{R Packages}
\vspace{-3ex}

%\begin{lonelist}
    %\item 
    Creator, \texttt{escheR} {\it Unified multi-dimensional visualizations with Gestalt principles}\\
    \url{https://github.com/boyiguo1/escheR}\\

    
    Creator, \texttt{BHAM} {\it Scalable Bayesian hierarchical additive models using spike-and-slab  priors for high-dimensional data analysis}\\
    \url{https://github.com/boyiguo1/BHAM}\\
    
	%\item 
	Creator, \texttt{MOTE.RF} {\it Random forests algorithm to infer treatment effect for multivariate outcome}\\
	\url{https://github.com/boyiguo1/MOTE.RF}\\
	
	%\item 
	Contributor, \texttt{BhGLM} {\it Fast-computing Bayesian Hierarchical GLMs and survival model}
	\url{https://github.com/nyiuab/BhGLM}\\
	
	%\item 
	Contributor, \texttt{TibbleOne} {\it Convenient framework to tabulate participant characteristics for epidemiology studies}\\
	\url{https://github.com/bcjaeger/tibbleOne}\\
%\end{lonelist}